Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome

### 2016-06-03 submission/Sze_Obesity_mBio_2016.tex
Trying to get table to render in pdf

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

>>>>

\documentclass[12pt,]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
    \usepackage{xltxtra,xunicode}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Mapping=tex-text,Scale=MatchLowercase}
  \newcommand{\euro}{€}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\usepackage[margin=1.0in]{geometry}
\ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
\else
  \usepackage[unicode=true]{hyperref}
\fi
\hypersetup{breaklinks=true,
            bookmarks=true,
            pdfauthor={},
            pdftitle={Looking for a Signal in the Noise: Revisiting Obesity and the Microbiome},
            colorlinks=true,
            citecolor=blue,
            urlcolor=blue,
            linkcolor=magenta,
            pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{longtable,booktabs}
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

@@

\begin{verbatim}
## 
## > capwords <- function(s, strict = FALSE) {
## +     s <- as.character(s)
## +     cap <- function(s) paste(toupper(substring(s, 1, 1)), {
## +         s <- su .... [TRUNCATED] 
## 
## > make_study_label <- function(dataset) {
## +     study <- ifelse(dataset == "hmp", "HMP", capwords(dataset))
## + }
## 
## > format_p <- function(p_value) {
## +     char_p <- format(round(p_value, 3), nsmall = 3)
## +     if (p_value < 0.001) {
## +         char_p <- "<0.001"
## +    .... [TRUNCATED] 
## 
## > get_study_summary <- function(study, beta = beta_summary) {
## +     metadata_file <- paste0("data/", study, "/", study, ".metadata")
## +     metadata <- .... [TRUNCATED] 
## 
## > beta_summary <- read.table("data/process/beta_tests.summary", 
## +     header = T, row.names = 1)
## 
## > datasets <- sort(rownames(beta_summary))
## 
## > study_summary <- t(sapply(datasets, get_study_summary))
## 
## > table1 <- kable(study_summary, row.names = FALSE, 
## +     col.names = c("Study", "Subjects (N)", "Obese (%)", "Average BMI (Min-Max)", 
## +         "Fe ..." ... [TRUNCATED]
\end{verbatim}

\begin{longtable}[c]{@{}lccccccc@{}}
\toprule
Study & Subjects (N) & Obese (\%) & Average BMI (Min-Max) & Female (\%)
& Average Age (Min-Max) & Non-Hispanic White (\%) & AMOVA
(P-value)\tabularnewline
\midrule
\endhead
Baxter & 172 & 27.3 & 27.0 (17.5-46.9) & 64.5 & 54.3 (29.0-80.0) & 87.8
& 0.078\tabularnewline
Escobar & 30 & 33.3 & 27.4 (19.5-37.6) & 46.7 & 38.1 (21.0-60.0) & NA &
0.047\tabularnewline
Goodrich & 982 & 19.7 & 26.3 (16.2-52.4) & 98.9 & 61.0 (23.0-86.0) & NA
& \textless{}0.001\tabularnewline
Hmp & 287 & 10.8 & 24.3 (19.0-34.0) & 49.1 & 26.3 (18.0-40.0) & 81.5 &
0.322\tabularnewline
Ross & 63 & 60.3 & 31.6 (22.1-47.9) & 76.2 & 57.0 (33.0-81.0) & 0.0 &
0.845\tabularnewline
Schubert & 104 & 32.7 & 28.2 (18.5-62.5) & 66.3 & 52.8 (19.0-88.0) &
82.7 & 0.180\tabularnewline
Turnbaugh & 146 & 67.8 & NA & NA & NA & 51.4 & 0.040\tabularnewline
Wu & 64 & 7.8 & 24.3 (14.0-41.3) & 53.1 & 26.3 (2.16-50.0) & NA &
0.577\tabularnewline
Zeevi & 731 & NA & 26.4 (16.4-47.0) & NA & 43.4 (18.0-70.0) & NA &
0.135\tabularnewline
Zupancic & 207 & 36.2 & 28.2 (18.2-127.0) & 57.0 & 46.7 (20.0-79.0) &
100.0 & 0.206\tabularnewline
\bottomrule
\end{longtable}
